\section{Introduction}


\subsection{Purpose}
The purpose of this document is to specify a software for Android users enabling the functionality to gather, organize and read feeds, regardless of if it is a RSS\cite{rss-spec}, ATOM\cite{atom}, Podcasts or social medium feed. Furthermore, this specification will act as base for the design document. This will be the first release of the mentioned software which is completely standalone in the sense that it is not part of a larger system.


\subsection{Intended Audience and Reading Suggestions}
The intended audience for this document are those with an engineering background interested in this project, whether it be the actual teacher assigning this project to the project group, one of the group members or an actual user wanting to know more about the product or continue development. The document is divided into two major sections. Section~\ref{sec:dev_environ} is about the development environment in which the product will be developed and section~\ref{sec:specifications} describes the classes and their connection as well as mock-ups of the user interface.


\subsection{Definitions, acronyms and abbreviations}
Below is a list of definitions, acronyms and abbreviations referenced in this document, sorted after appearance.

\begin{description}
  \item[API] \hfill \\
  Application Programming Interface
\end{description}


\subsection{References}
In this section is a list of all documents referenced throughout the rest of this document.

\bibliography{ref}
\bibliographystyle{unsrt}