\section*{Revision History}
\begin{center}
    \begin{tabularx}{\linewidth}{ | l | l | X | l |}
    \hline
    Version & Date & Description & Author\\ \hline
    0.1 & 24-Oct-2012 & First draft, an empty skeleton. & T. Ingvarsson\\ \hline
    0.2 & 24-Oct-2012 & Added initial section structure. & T. Ingvarsson\\ \hline
    0.10 & 28-Oct-2012 & Added entity and class diagrams along with initial descriptions. Also added the introduction content. & T. Ingvarsson\\ \hline
    0.11 & 28-Oct-2012 & Added content to Development Environment. & I. Trun\\ \hline
    0.12 & 30-Oct-2012 & Added User Interfaces. & B. Pohl\\ \hline
    0.13 & 30-Oct-2012 & Added Task distribution. Corrected and cleaned up Development Environment, included references for tools as well as cost estimation. & T. Ingvarsson\\ \hline
    0.20 & 20-Nov-2012 & Removed the user interfaces, as to prepare for them to be along with their respective system feature. Added the required subsections for the design phase; Overall Architecture, Directory Organization and Class Description. Also started filling the subsections. & T. Ingvarsson\\ \hline
    0.21 & 21-Nov-2012 & Finished class descriptions. & T. Ingvarsson\\ \hline
    0.22 & 26-Nov-2012 & Updated and simplified architecture diagram. Added system feature; View Statistics. & T. Ingvarsson\\ \hline
    0.23 & 28-Nov-2012 & Updated Specification section with some small changes, also added use cases including screenshots for the system features. & T. Ingvarsson\\ \hline
     & & & \\ \hline
    % copy the last line before adding the new revision.
    \end{tabularx}
    
    % new page of revision history
%    \begin{tabularx}{\linewidth}{ | l | l | X | l |}
%    \hline
%    Version & Date & Description & Author\\ \hline
%     &  &  &  \\ \hline
%    % copy the last line before adding the new revision.
%    \end{tabularx}
\end{center}