\section*{Revision History}
\begin{center}
    \begin{tabularx}{\linewidth}{ | l | l | X | l |}
    \hline
    \textbf{Version} & \textbf{Date} & \textbf{Description} & \textbf{Author}\\ \hline
    0.1 & 09-Oct-2012 & First draft. & T. Ingvarsson\\ \hline
    0.11 & 09-Oct-2012 & Added Revision History and Table of Contents. & T. Ingvarsson\\ \hline
    0.12 & 09-Oct-2012 & Detailed Requirements table has been remade into a multi-page table. & T. Ingvarsson\\ \hline
    0.13 & 14-Oct-2012 & Stream-lined the abstract and introduction to not have too much redundancy. & T. Ingvarsson\\ \hline
    0.14 & 15-Oct-2012 & Software Interfaces is rewritten as pure requirements that do not imply how it should be solved. & T. Ingvarsson \\ \hline
    0.15 & 15-Oct-2012 & Major overhaul of User Interfaces. Simplified and removed unnecessary descriptions. To strict requirements are removed at this stage. & T. Ingvarsson\\ \hline
    0.16 & 15-Oct-2012 & Major overhaul of Product Features. Added a use case diagram including a better overview of the features as well as a list of actors to the system. & T. Ingvarsson\\ \hline
    0.17 & 16-Oct-2012 & Simplified the System Features section by removing the functional requirements of every subsection, this will be covered in the detailed requirement list anyway. Removed feed list and all with it, is not a feature requirement.  Removed subsection Manage Categories as this is covered in Manage Feeds. & T. Ingvarsson\\ \hline
    0.18 & 19-Oct-2012 & Added References. & T. Ingvarsson\\ \hline
    0.19 & 23-Oct-2012 & Added Software Quality Attributes to Other Non-functional Requirements. & T. Ingvarsson\\ \hline
    0.20 & 23-Oct-2012 & Updated use case diagram with more sub-features. Updated System Features to match the use case diagram. & T. Ingvarsson\\ \hline
    % copy the last line before adding the new revision.
    \end{tabularx}
    
    % new page of revision history
    \begin{tabularx}{\linewidth}{ | l | l | X | l |}
    \hline
    \textbf{Version} & \textbf{Date} & \textbf{Description} & \textbf{Author}\\ \hline
    0.21 & 24-Oct-2012 & Update the Detailed Requirement list to match the rest of the updates. & T. Ingvarsson\\ \hline
    0.22 & 27-Oct-2012 & Added new features; Share Post, Import Feed(s), Export Feed(s), Find Similar Feed(s). Changed so it should handle multiple kinds of sources, not just RSS. & T. Ingvarsson\\ \hline
    0.30 & 21-Nov-2012 & Added comparison table of the most popular readers existing on the Google Play Store to clarify the differences. & T. Ingvarsson\\ \hline
    0.31 & 26-Nov-2012 & Added a system feature; gather and display statistics. Also updated the deadlines mentioned under project constraints. & T. Ingvarsson\\ \hline
     &  &  & \\ \hline
    % copy the last line before adding the new revision.
    \end{tabularx}
\end{center}