\section{System Interface}


\subsection{User Interfaces}
The product shall provide a set of views enabling the user to all system features. 

\subsubsection{Main View}
The product shall be able to list all categories in alphabetic order, clicking on a category shall take the user to the \textit{Feeds View} for that specific category. The view shall include the following options:

\begin{itemize}
  \item Add category
  \item Remove category
  \item Add feed
  \item Fetch posts
\end{itemize}
The first entry in the list should be a \textit{View all\ldots} button that should show the latest posts from all feeds in all categories. The last entry in the list should be a \textit{Add Category\ldots} button.


\subsubsection{Category View}
The product shall be able to list all feeds for a specific category in alphabetic order, clicking on a feed shall take the user to the \textit{Posts View} for that specific feed. The view shall include the following options:

\begin{itemize}
  \item Add feed
  \item Remove feed
  \item Remove active category
  \item Fetch posts
\end{itemize}
The first entry in the list should be a \textit{View All\ldots} button that should show the latest posts from all feeds in the specific category. The last entry in the list should be a \textit{Add Feed\ldots} button.


\subsubsection{Feed View}
The product shall be able to list the latest posts for a specific feed in a latest first order. Clicking on a post shall take the user to the \textit{Post View} for that specific post. The posts shall be displayed with their heading. The view shall include the following options:

\begin{itemize}
  \item Mark all posts as read/unread
  \item Remove active feed
  \item Fetch posts
\end{itemize}
The last entry in the list should be a \textit{Older Posts\ldots} button that should fetch older posts to show.


\subsubsection{Post View}
The product shall be able to display a specific post and all of its content. The view should enable sliding; sliding the screen to the right should show a older post, while sliding to the left should show a newer post. 


\subsection{Software Interfaces}


\subsubsection{Internet}
The product shall require access to Internet so that RSS feeds can be accessed and posts be downloaded. RSS feeds shall be accessed through either HTTP or FTP.


\subsubsection{External Memory}
The product should be able to store settings, feed lists and posts on an external memory. It should be able to both store and remove files. 


\subsubsection{Background Task}
The product should periodically update; download new posts and delete old ones. If the product's main interface is active it shall make sure that an opened post is not deleted.


\subsubsection{Notification Bar}
The product should be able to notify the user that there are new posts through the notification bar. It should also show the amount of un-read posts.